Modeling the impacts of replacing car trips with combined public transport and cycling: \ Reproducible methods, results and actionable evidence from biclaR

### 2024-04-17 paper/PaperCEUS/PaperCEUS_rev1.Rmd
Create PaperCEUS_rev1.Rmd

Emission factors are estimated for the following air pollutants: CO, NO~X~, VOC, and PM. Emission factors of the main greenhouse gases (GHG) are also estimated: CO~2~, CH~4~ and N~2~O, converted in CO~2~eq by the following relationship[^9]: $EF_{CO_2eq} = EF_{CO_2} + 28\cdot EF_{CH_4} + 265\cdot EF_{N_2O}$.
The CH~4~ and N~2~O emission factors do not vary with travel speed.
The PM10 emission factor does not vary with trip distance.

@@

The conversion of avoided emissions into avoided welfare loss and respective monetary valuation was based on the EU Guide to Cost-benefit Analysis [@EuropeanCommission2014] and the best up-to-date reference values for the various gases [@EuropeanCommission2014; @bickel2006; @UNITE]: 8.44 €/ton for CO, 2,867.85 €/ton for NO~X~, 340,969.27 €/ton for PM10, 7,169.62 €/ton for VOC and 35.85 €/ton for CO~2~eq.
The social impacts are in avoided premature mortality. This result is finally monetized using the *Statistical Value of Life* for Portugal: €3,055,358/fatality [@ANSR2021].
We updated all the monetary reference values of the literature based on the annual inflation rate in Portugal for 2022[^7], and our 10-years estimations assumed a discount rate of 5% and inflation of 3%. 
See [Research Data](#research-data) for all the input values we used.

@@

<!-- FOR OTHER PAPER: separate the Socio impacts from the Environmental ones? -->
Shifting from car to cycling in combination with PT can reduce annual CO~2~eq emissions by 14,000 to 36,000 tons per year. 
The 10-year socio-environmental benefits account for €125 million to €325 million, depending on the cycling targets.

@@

## Acknowledgements {.unnumbered}
[*blind*]
<!-- This research was funded by the Lisbon's Metropolitan Department of Transport (TML - Transportes Metropolitanos de Lisboa, E.M.T., S.A.), under the *biclaR* Project. -->
<!-- This work is part of the research activity carried out at Civil Engineering Research and Innovation for Sustainability (CERIS) and has been funded by Fundação para a Ciência e a Tecnologia (FCT), Portugal in the framework of project UIDB/04625/2020. -->
<!-- The authors thank Thomas Götschi (HEAT for Cycling) for providing access to _HaaS_ tool, which is under development. -->

## Research data {.unnumbered}
The data and the code to reproduce the results will be made available upon publication.

>>>>

Emission factors are estimated for the following air pollutants: CO, NO~X~, VOC, and PM~10~. Emission factors of the main greenhouse gases (GHG) are also estimated: CO~2~, CH~4~ and N~2~O, converted in CO~2~eq by the following relationship[^9]: $EF_{CO_2eq} = EF_{CO_2} + 28\cdot EF_{CH_4} + 265\cdot EF_{N_2O}$.
The CH~4~ and N~2~O emission factors do not vary with travel speed.
The PM~10~ emission factor does not vary with trip distance.

@@

The conversion of avoided emissions into avoided welfare loss and respective monetary valuation was based on the EU Guide to Cost-benefit Analysis [@EuropeanCommission2014] and the best up-to-date reference values for the various gases [@EuropeanCommission2014; @bickel2006; @UNITE]: 8.44 €/ton for CO, 2,867.85 €/ton for NO~X~, 340,969.27 €/ton for PM~10~, 7,169.62 €/ton for VOC and 35.85 €/ton for CO~2~eq.
The social impacts are in avoided premature mortality. This result is finally monetized using the *Statistical Value of Life* for Portugal: €3,055,358/fatality [@ANSR2021].
We updated all the monetary reference values of the literature based on the annual inflation rate in Portugal for 2022[^7], and our 10-years estimations assumed a discount rate of 5% and inflation of 3%. 
See [Research Data](#research-data) for all the input values we used.

@@

<!-- FOR OTHER PAPER: separate the Socio impacts from the Environmental ones? -->
Shifting from car to cycling in combination with PT can reduce annual CO~2~eq emissions by 11,500 to 28,500 tons per year. 
These figures represent a 2.7% reduction in Lisbon's transport emissions [@LisboaENova], a small but important component of wider transport decarbonization measures.
The 10-year socio-environmental benefits account for €125 million to €325 million, depending on the cycling targets.

@@

# Acknowledgements {.unnumbered}
[*blind*]
<!-- This research was funded by the Lisbon's Metropolitan Department of Transport (TML - Transportes Metropolitanos de Lisboa, E.M.T., S.A.), under the *biclaR* Project. -->
<!-- This work is part of the research activity carried out at Civil Engineering Research and Innovation for Sustainability (CERIS) and has been funded by Fundação para a Ciência e a Tecnologia (FCT), Portugal in the framework of project UIDB/04625/2020. -->
<!-- The authors thank Thomas Götschi (HEAT for Cycling) for providing access to _HaaS_ tool, which is under development. -->

# Research data {.unnumbered}
The data and the code to reproduce the results will be made available upon publication.
